SIMITAR: realistic and autoconfigurable traffic generation

### 2017-11-30 Docs/PaperSimitar/header.tex
new files

%\title{Paper Title*\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
%}
\title{Using BIC and AIC for Ethernet traffic model selection. Is it worth?}

@@

\begin{abstract}
In this work, we aim to evaluate how good are the information criteria AIC and BIC inferring which is the best stochastic process to describe Ethernet inter-packet times. Also, we check if there is a practical difference between using AIC or BIC. We use a set of stochastic distributions to represent inter-packet of a traffic trace and calculate AIC and BIC. To test the quality of  BIC and AIC guesses,  we define a cost function based on the comparison of significant stochastic properties for internet traffic modeling, such as correlation, fractal-level and mean. Then, we compare both results.  In this short paper, we present just the results of a public free Skype-application packet capture, but we provide as reference further analyzes on different traffic traces. We conclude that for most cases AIC and BIC can guess right the best fitting according to the standards of Ethernet traffic modeling.
\end{abstract}

\begin{IEEEkeywords}
BIC, AIC, stochastic function, inter-packet times, correlation, Hurst exponent, heavy-tailed distribution, fractal-level, burstiness, linear-regression, weibull, pareto, exponential, normal, poison, maximum likelihood, Ethernet traffic, traffic modeling, fractal-level, pcap file, Skype traffic.
\end{IEEEkeywords}

>>>>

%\title{Paper Title*\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
%}
\title{SIMITAR: realistic and autoconfigurable traffic generation}

@@

\begin{abstract}
It is a well known fact that the type of traffic on network measurements matters. A realistic Ethernet have a different impact compared to constant traffic tools like Iperf, even with the same bandwidth. A burstier traffic may cause buffers overflows when a constant traffic does not, decrease on the measurement acuracy. The number of flows of a traffic may have an impact of flow-oriented nodes, such as SDN switches and controllers. Today in an scenario where software defined networks are going to play an essential role in the future of the networks, a depper validation of new technologies in order to guarantee the SLAs is crucial. In this scenario we come with an anternative for realist traffic generation. Most of open-source realistic traffic generator tools have the modelling layer coupled to the traffic generator API, wich make it difficult to be update to newer lybraries, or require user programming and manual configuration. We propose a sollution called SIMITAR: SnIffing, ModellIng and TrAffic geneRation, that have a separated moddelling framework from the traffic generator, which is flow-oriented, and is autoconfigurable. It creates and use as imputs compact traces descriptos, XML files that describes all features of the traffics. 
Currently we are able to replicate with acuracy 
\end{abstract}

\begin{IEEEkeywords}
Sniffing, traffic modelling, BIC, AIC, inter-packet times, Wavelet scalling, traffic generator, Burstiness, pcap file, linear regression, Iperf
\end{IEEEkeywords}
